Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-09-23 head.tex
reconstruct logically

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In the Cloud Manufacturing Ecosystem, a benign mode and methodology for massive services schedule is
required, in order for the collaboration within the whole Industry Chain. This paper studied the data of the
resources and services and modeled the services scheduling problem in the chain. With the Big Data
analysis on the Cloud Platform, optimal assessment/schedule methods were developed, which could
gradually evolve the ecosystem to an optimal situation. 
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Cloud Manufacturing \sep Ecosystem \sep scheduling
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

>>>>

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were contructed by resources is required, in order for the collaboration within the whole Industry Chain.
This paper 
\begin{inparaenum}[1)]
\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
\item modeled the services scheduling matter in the chain;
\item designed a simulation for the Cloud Manufacturing Ecosystem;
\item opened some Ecosystem related issues. 
\end{inparaenum}
With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
gradually evolve the ecosystem to an optimal situation.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Cloud Manufacturing \sep Ecosystem \sep simulation \sep scheduling \sep optimization
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}
